The Cluster Difference Imaging Photometric Survey (CDIPS). I. Light Curves \& Planet Candidates in Open Clusters from TESS Sectors 6 \& 7

### 2019-06-28 paper/ms.tex
update text for above

The physical parameters quoted in Table YYY, and on exofop-TESS,
should be considered preliminary, and could be substantially improved
with an object-by-object analysis.  A few additional assumptions were
required to report some of the values.  For the stellar radii, we
assumed the $R_\star$ values and uncertainties reported in the TIC.
There were a few cases with null uncertainties in the stellar radii --
for these, we simply invented a relative uncertainty of 30\%, and note
in the comments that this was done.  The uncertainties in e.g., the
planetary radii and impact parameters were found using linear error
propagation theory, under the idealized assumption that the covariance
between all stellar and planetary parameters was zero.

Finally, the determine the names of the objects -- that is whether
they were already TOIs, or cTOIs -- we cross-referenced based on a
combination of the TIC identifier, spatial position, and the ephemeris
of each object.

>>>>

The physical parameters quoted in Table YYY, and on exofop-TESS,
should be considered preliminary, and could be substantially improved
with an object-by-object analysis.  A few additional assumptions were
required to report some of the values.  For the stellar radii, we
assumed the $R_\star$ values and uncertainties reported in the TIC.
There were a few cases with null uncertainties in the stellar radii --
for these, we simply invented a relative uncertainty of 30\%, and note
in the comments that this was done.  There were also a few cases for
which the TIC stellar temperatures and/or radii were not available,
but the Gaia values were.  In these cases, we used the Gaia $T_{\rm
eff}$ and $R_\star$ values, and used the stellar mass interpolated
from the \citet{pecaut_intrinsic_2013} table (assuming the star is a
dwarf) to estimate $\log g$.  The uncertainties in e.g., the planetary
radii and impact parameters were found using linear error propagation
theory, under the idealized assumption that the covariance between all
stellar and planetary parameters was zero.

Finally, the determine the names of the objects -- and whether they
had already been identified as TOIs or cTOIs -- we cross-referenced
based on a combination of the TIC identifier, spatial position, and
the ephemeris of each object.
